Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-03-24 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
update Fuchs information & fix affiliations and citations

\author{Alexandru Botan}
%\affiliation{The authors are listed in alphaphetical order.}
%\affiliation{The author list is not completed.}
\affiliation[Lyon CNRS]{Institut Lumi\`ere Mati\`ere, UMR5306 Universit\'e Lyon 1-CNRS, Universit\'e de Lyon 69622 Villeurbanne, France}
%
%\author{Andrea Catte}
%\affiliation{University of East Anglia, Norwich, United Kingdom}
\author{Fernando Favela-Rosales}
\affiliation[Mexico]{Departamento de F{\'i}sica - CINVESTAV}
\author{Patrick Fuchs}
\affiliation[CNRS paris]{Institut Jacques Monod, CNRS, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, Paris, France}
\alsoaffiliation[Diderot University]
{Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, Paris, France}
\author{Matti Javanainen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Waldemar Kulig}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Antti Lamberg}
\affiliation[Kyoto University]
{Department of Chemical Engineering, Kyoto University, Kyoto, Japan}
\author{Markus S. Miettinen}
\affiliation[Freie Universitat Berlin] 
{Fachbereich Physik, Freie Universitat Berlin, Berlin, Germany}
\author{Luca Monticelli}
\affiliation[UMR] 
{5IBCP, CNRS UMR 5086, Lyon, France}
\author{Jukka Maatta}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{O. H. Samuli Ollila} 
\email{samuli.ollila@aalto.fi.}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{Marius Retegan}
\affiliation[Max Planck]
{Max Planck Institute for Chemical Energy Conversion, Mulheim an der Ruhr, Germany}
\author{Tomasz Rog}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Hubert Santuz}
\affiliation[INSERM]
{INSERM, U1134, DSIMB; Institut National de la Transfusion Sanguine (INTS); Laboratoire d'Excellence GR-Ex, Paris, France}
\alsoaffiliation[Diderot]
{Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, Paris, France}
\author{Joona Tynkkynen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{refs}

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} \\
{\it Fernando Favela}  \\
{\it Patrick Fuchs} \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli}  \\
{\it Jukka Maatta}  \\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog}  \\
{\it Hubert Santuz}  \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\

@@

%\newpage
\end{document}

>>>>

\author{Alexandru Botan}
%\affiliation{The authors are listed in alphaphetical order.}
%\affiliation{The author list is not completed.}
\affiliation[Lyon CNRS]{Institut Lumi\`ere Mati\`ere, UMR5306 Universit\'e Lyon 1-CNRS, Universit\'e de Lyon 69622 Villeurbanne, France}
%
%\author{Andrea Catte}
%\affiliation{University of East Anglia, Norwich, United Kingdom}
\author{Fernando Favela-Rosales}
\affiliation[Mexico]{Departamento de F{\'i}sica - CINVESTAV}
\author{Patrick F. J. Fuchs}
\affiliation[CNRS Paris]{Institut Jacques Monod, CNRS, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, Paris, France}
%\alsoaffiliation[Diderot University]
%{Institut Jacques Monod, CNRS UMR 7592, Universit{\'e} Paris Diderot, Sorbonne Paris Cit{\'e}, Paris, France}
\author{Matti Javanainen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Waldemar Kulig}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Antti Lamberg}
\affiliation[Kyoto University]
{Department of Chemical Engineering, Kyoto University, Kyoto, Japan}
\author{Markus S. Miettinen}
\affiliation[Freie Universitat Berlin] 
{Fachbereich Physik, Freie Universitat Berlin, Berlin, Germany}
\author{Luca Monticelli}
\affiliation[UMR] 
{5IBCP, CNRS UMR 5086, Lyon, France}
\author{Jukka Maatta}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{O. H. Samuli Ollila} 
\email{samuli.ollila@aalto.fi.}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{Marius Retegan}
\affiliation[Max Planck]
{Max Planck Institute for Chemical Energy Conversion, Mulheim an der Ruhr, Germany}
\author{Tomasz Rog}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Hubert Santuz}
\affiliation[INSERM]
{INSERM, U1134, DSIMB; Institut National de la Transfusion Sanguine (INTS); Laboratoire d'Excellence GR-Ex, Paris, France}
\alsoaffiliation[Diderot]
{Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, Paris, France}
\author{Joona Tynkkynen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} \\
{\it Fernando Favela}  \\
{\it Patrick F. J. Fuchs} Ran and analyzed the Poger simulations. Provided scientific information which significantly advanced the project (signs and forking of order parameters). \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli}  \\
{\it Jukka Maatta}  \\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog}  \\
{\it Hubert Santuz}  \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\

@@

%\newpage

\bibliography{refs}

\end{document}
